\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2019-01-21 bare_conf.tex
small typo fix.

However, some types of guidance information may be more efficiently perceived through tactile feedback device than audio channel. For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description. More research is needed to clarify how various types of guidance information should be represented to the user in the most convenient and efficient way \textcolor{red}{ For instance, the detected objects could be presented to the user in a configurable order, based on the subjective importance of particular object classes or other personalized criteria.} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.

@@

\bibitem{Valor} G. Varol, I. Laptev, and C. Schmid. Long-Term Temporal Convolutions for Action Recognition.  IEEE Transactions on Pattern Analysis and Machine Intelligence. Vol. 40, issue 6, pp. 1510 - 1517, 2016.

>>>>

However, some types of guidance information may be more efficiently perceived through tactile feedback device than audio channel. For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description. More research is needed to clarify how various types of guidance information should be represented to the user in the most convenient and efficient way. \textcolor{red}{ For instance, the detected objects could be presented to the user in a configurable order, based on the subjective importance of particular object classes or other personalized criteria.} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.

@@

\bibitem{Valor} G. Varol, I. Laptev, and C. Schmid. Long-Term Temporal Convolutions for Action Recognition.  IEEE Transactions on Pattern Analysis and Machine Intelligence. Vol. 40, issue 6, pp. 1510-1517, 2016.
